\section{Protest Procedure}\label{sec:protest_procedure}

For all competition categories, procedure of protest shall be governed by the following rules:
\begin{legal}
\item  The Team Manager must file a protest by filling in a form provided by Competition Secretary\\

A request for the `protest form' for all categories must be made within 10 minutes after result of the competition has been announced; and within the following 20 minutes, the completed form must be returned to the Competition Secretary including the protest fee of USD200.00 in cash.

\item In filing a protest, objections must be clearly described.\\

At the first level, the protest will be handled by the Competition Chairperson together with the Council of Referee-Jury. The decision will be conveyed to the Team Manager within 2 (two) hours after the protest is submitted.

\item  If the decision made at first level is not accepted, the Team Mananager may make an appeal. The appeal should be made within 20 minutes after the first-level decision is received.

\item The Appeal Committee shall consists of the International Technical Delegate as the Chairperson, and Competition Chairperson and Council of Referee-Jury Council as members. They will review the case and make decision within 3 (three) hours after the appeal is received. At this level, the decision is final.

\item A protest may be reviewed only if it is submitted properly according to the noble values and ethics of Pencak Silat.

\item  Every protest will be imposed with USD 200 fee, unless USSSA/PERSILAT stipulates otherwise. The protest fee is given to Competition Chairperson through Competition Secretary and will be used for Competition Officials (International Technical Delegate, Competition Chairperson, Council of Referee-Jury and Referee-Jury).
\end{legal}

\section{Technical Meeting}
\label{sec:technical_meeting}

\begin{legal}
\item Technical Meeting must be held before the start of the competition.
\item The meeting is presided by Competition Chairperson accompanied by the ITD and/or
ATD, the Council of Referee-Jury and the Chairperson/representative of the Organizing
Committee.
\item Attended by Team Managers and/or Team Coaches.
\item The meeting agenda is a general explanation on competition matters and balloting
process.
\item If necessary, the Competition Committee may conduct a consultative meeting with
the Team Managers at any time during the championship.
\end{legal}
